Decomposing labelled proof theory for~intuitionistic~modal~logic

### 2020-08-31 FullyLabelled/JLC/introduction.tex
adding more TODO
working on reviews

Besides that, there is another pleasant observation to make about our
system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multiple-conclusion systems in nested
sequents~\cite{str:2017maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
intuitionistic logic. 
%
Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
%
Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
%
This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.

@@

%\todo{maybe paragraph on related work?}

>>>>

Besides that, there is another pleasant observation to make about our
system. Ordinary labelled sequent systems for intuitionistic modal
logic are single-conclusion~\cite{simpson:phd}. 
%
The same is true for the corresponding nested sequent
systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
Maehara style multiple-conclusion systems in nested
sequents~\cite{str:2017maehara}, and therefore also in ordinary
labelled sequents. However, also in these systems there are rules
($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
premise, even though this is not the case in labelled
systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
intuitionistic logic. 
%

\review{The rules of their calculus are identical (except for the ones that relate the two accessibility relations) to the rules for the intuitionistic-alethic fragment	of the calculus for intuitionistic bimodal logic in this publication:
	• Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
%
\marianela{
Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
%
This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.  Furthermore, we present in this contribution an internal cut elimination proof.}

@@

\todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
%\todo{maybe paragraph on related work?}
